Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-17 analysis/paper/paper.Rmd
Install package dependencies to knit paper
spelling/punctuation correction

install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org")

@@

Model fitnesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].

>>>>

install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)

@@

Model fitness's were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
